Frequent Payment \thanks{}

### 2019-08-20 main.tex
grf

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_num_p.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_sum_porcp_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_dias_al_desempenyo.pdf}
    \end{subfigure}    
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
\end{figure}

>>>>

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_num_p.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_sum_porcp_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_dias_al_desempenyo.pdf}
    \end{subfigure}    
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
\end{figure}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect for Paid Loan Branches}
    \label{Treatment Effect branch}
    \begin{center}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_3.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_3.pdf}
    \end{subfigure}
     \begin{subfigure}{0.3\textwidth}
      \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_4.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_dist_des_c_pro_5.pdf}
    \end{subfigure} 
    \begin{subfigure}{0.3\textwidth}
        \caption{x}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_5.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
\end{figure}
